
```{r}
plot(cars)
names(Base1)
Base1[,-c(7,9,11,16,18,35)] =NULL
Base1
```


```{r}
Base1$prov->Base1$Departamento
Base1$perprov->Base1$Provincia
Base1$ur->Base1$Zona
Base1$q1->Base1$Sexo
Base1$q2->Base1$Edad
Base1$cp13->Base1$AsistPartiPolit
Base1
```


```{r}
Base1[,c(1,2,3,4,5,6)]=NULL
Base1
```


```{r}
Base1$Zona <- gsub("1","Urbano",Base1$Zona)
Base1$Zona <- gsub("2","Rural",Base1$Zona)

Base1$Sexo <- gsub("1","Hombre",Base1$Sexo)
Base1$Sexo <- gsub("2","Mujer",Base1$Sexo)
Base1$AsistPartiPolit <- gsub("1","Una vez a la semana",Base1$AsistPartiPolit)
Base1$AsistPartiPolit <- gsub("2","Una o dos veces al mes",Base1$AsistPartiPolit)
Base1$AsistPartiPolit <- gsub("3","Una o dos veces al año",Base1$AsistPartiPolit)
Base1$AsistPartiPolit <- gsub("4","Nunca",Base1$AsistPartiPolit)
Base1
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
